---
title: "Cluster analysis - workflow: 1. Missingness and imputation"
author: "Karl Gisslander"
date: "2024-02-21"
output: html_document
---

### Import and list relevant libraries
```{r echo=FALSE}
library(tidyverse)
library(naniar)
library(lubridate)
library(mice)
library(ggmice)
```

### Set up working directory and import data
```{r}
czech <- read.csv("Czech/czech_prepared.csv")
fvsg <- read.csv("FVSG/fvsg_prepared.csv")
gevas <- read.csv("Gevas/gevas_prepared.csv")
polvas <- read.csv("Polvas/polvas_prepared.csv")
rkd <- read.csv("RKD/rkd_prepared.csv")
skane <- read.csv("Skåne/skane_prepared.csv")

```

### Merge all dataframes to one.
```{r}
data <- rbind(czech, fvsg, gevas, polvas, rkd, skane)
```

### Create a matrix with the variables we need for the imputation. We set variables in correct class and fix it to fit clustMD later.
```{r}
# dplyr::select the variables of interest
matrix <- data %>%
  dplyr::select(id, age, creatinine, crp, gender, constitutional, musculoskeletal, cutaneous, eye, mucosa,
           ent, chest, cardio, abdominal, kidney, cns, pns, anca, dateofdiagnosis, death, dateofdeath, eskd, dateofeskd, dateoffollowup, maindiagnosis, registry)

# We set up some time to event information. I think it's best if we write this as time of follow up and use the death = TRUE/FALSE and eskd = TRUE/FALSE as censoring. 
matrix <- matrix %>%
  mutate(timeoffollowup = as.numeric(floor(time_length(difftime(dateoffollowup, dateofdiagnosis), "days"))))

matrix <- matrix %>%
  mutate(dateoffollowup_eskd = case_when(!is.na(dateofeskd) ~ dateofeskd,
                                          .default = dateoffollowup))

matrix <- matrix %>%
  mutate(timeoffollowupeskd = as.numeric(floor(time_length(difftime(dateoffollowup_eskd , dateofdiagnosis), "days"))))

# We keep the event information we want for the imputation
matrix <- matrix %>%
  dplyr::select(id, age, creatinine, crp, gender, constitutional, musculoskeletal, cutaneous, eye, mucosa,
           ent, chest, cardio, abdominal, kidney, cns, pns, anca, death, timeoffollowup, eskd, timeoffollowupeskd, maindiagnosis, registry)

# Tranform strings to numbers for relevant variables
matrix <- matrix  %>% 
  mutate(gender = case_when(gender == "Male" ~ 0,
                            gender == "Female" ~ 1)) %>%
  mutate(anca = case_when(anca == "ANCA negative" ~ 1,
                              anca == "MPO positive" ~ 2,
                              anca == "PR3 positive" ~ 3))

# Define the classes of the matrix
matrix <- matrix  %>% 
  mutate(age = as.numeric(age)) %>%
  mutate(creatinine = as.numeric(creatinine)) %>%
  mutate(crp = as.numeric(crp)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(constitutional = as.factor(constitutional)) %>%
  mutate(musculoskeletal = as.factor(musculoskeletal)) %>%
  mutate(cutaneous = as.factor(cutaneous)) %>%
  mutate(eye = as.factor(eye)) %>%
  mutate(mucosa = as.factor(mucosa)) %>%
  mutate(ent = as.factor(ent)) %>%
  mutate(chest = as.factor(chest)) %>%
  mutate(cardio = as.factor(cardio)) %>%
  mutate(abdominal = as.factor(abdominal)) %>%
  mutate(kidney = as.factor(kidney)) %>%
  mutate(cns = as.factor(cns)) %>%
  mutate(pns = as.factor(pns)) %>%
  mutate(anca = as.factor(anca)) %>%
  mutate(death = as.factor(death)) %>%
  mutate(timeoffollowup = as.numeric(timeoffollowup)) %>%
  mutate(eskd = as.factor(eskd)) %>%
  mutate(timeoffollowupeskd = as.numeric(timeoffollowupeskd)) %>%
  mutate(maindiagnosis = as.factor(maindiagnosis)) %>%
  mutate(registry = as.factor(registry))

# ClustMD requires a data matrix where the variables are ordered so that the continuous variables come first, the binary (coded 1 and 2) and ordinal variables (coded 1, 2, ...) come second and the nominal variables (coded 1, 2, ...) are in last position.
matrix <- matrix %>%
  mutate(gender = as.factor(case_when(gender == 1 ~ 2,
            gender == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(constitutional = as.factor(case_when(constitutional == 1 ~ 2,
            constitutional == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(musculoskeletal = as.factor(case_when(musculoskeletal  == 1 ~ 2,
            musculoskeletal  == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(cutaneous = as.factor(case_when(cutaneous == 1 ~ 2,
            cutaneous == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(eye = as.factor(case_when(eye == 1 ~ 2,
            eye == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(mucosa = as.factor(case_when(mucosa == 1 ~ 2,
            mucosa == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(ent = as.factor(case_when(ent == 1 ~ 2,
            ent == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(chest = as.factor(case_when(chest == 1 ~ 2,
            chest == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(cardio = as.factor(case_when(cardio == 1 ~ 2,
            cardio == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(abdominal = as.factor(case_when(abdominal == 1 ~ 2,
            abdominal == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(kidney = as.factor(case_when(kidney == 1 ~ 2,
            kidney == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(cns = as.factor(case_when(cns == 1 ~ 2,
            cns == 0 ~ 1,
            TRUE ~ NA)))
matrix <- matrix %>%
  mutate(pns = as.factor(case_when(pns == 1 ~ 2,
            pns == 0 ~ 1,
            TRUE ~ NA)))

```

### We explore missingness of data
```{r}
# Are there missing values in the dataset?
any_na(matrix[2:18])

# How many?
n_miss(matrix[2:18])
prop_miss(matrix[2:18])

# Which variables are affected?
matrix[2:18] %>%
  is.na() %>% 
  colSums()

```

```{r}
# Get number of missings per variable (n and %)
miss_var_summary(matrix[2:18])

# Get number of missings per participant (n and %)
miss_case_table(matrix[2:18])

# Where are missings located?
vis_miss(matrix[2:18]) + theme(axis.text.x = element_text(angle=80))

# Which combinations of variables occur to be missing together?
gg_miss_upset(matrix[2:18], nsets = 17, nintersects = 100)

```

### Removal of >50% missing data and shuffle rows
```{r}
# We make the relevant dataframe
frame <- matrix %>%
  dplyr::select(id, age, creatinine, crp, gender, constitutional, musculoskeletal, cutaneous, eye, mucosa,
           ent, chest, cardio, abdominal, kidney, cns, pns, anca)

# We make a dataframe containing information of potential relevance for imputation
matrix_2 <- matrix %>%
  dplyr::select(id, death, timeoffollowup, eskd, timeoffollowupeskd, maindiagnosis, registry)

# Remove cases with >50% missing data
frame <- frame[which(rowMeans(!is.na(frame)) > 0.5), ]

# Merge with relevant data for imputation
frame <- merge(frame, matrix_2, by = "id")

# Scramble rows
frame = frame[sample(1:nrow(frame)), ]

# Save this! This contains the row order. (It is in imputed sets as well but not used in imputation. See below)
write.csv(frame, "full_data_50.csv", row.names = FALSE)

```

### New missingness exploration
```{r}
# Are there missing values in the dataset?
any_na(frame[2:18])

# How many?
n_miss(frame[2:18])
prop_miss(frame[2:18])

# Which variables are affected?
frame[2:18] %>%
  is.na() %>% 
  colSums()

# Get number of missings per variable (n and %)
miss_var_summary(frame[2:18])

# Get number of missings per participant (n and %)
miss_case_table(frame[2:18])

# Where are missings located?
vis_miss(frame[2:18]) + theme(axis.text.x = element_text(angle=80))

# Which combinations of variables occur to be missing together?
gg_miss_upset(frame[2:18], nsets = 17, nintersects = 100)

pdf("missingness_plot.pdf")
missingness_plot <- gg_miss_upset(frame[2:18], nsets = 17, nintersects = 100)
print(missingness_plot)
dev.off()

```

### Set the predictor matrix, run imputation, explore results and print file
```{r}
ini <- mice(frame,maxit=0) # dry run without iterations to get the predictor matrix
pred1 <- ini$predictorMatrix # this is the predictor matrix
pred1[,'id'] <- 0 # set all id column values to zero to exclude it as a predictor

# Run mice with the predictior matrix above
imp <- mice(frame, print = FALSE, m = 10, pred = pred1) 

#Side-by-side box-and-whisker plots for the observed and synthetic data (continuous variables)
ggmice(imp, ggplot2::aes(x = .imp, y = age)) +
    ggplot2::geom_boxplot() 
ggmice(imp, ggplot2::aes(x = .imp, y = creatinine)) +
    ggplot2::geom_boxplot() 
ggmice(imp, ggplot2::aes(x = .imp, y = crp)) +
    ggplot2::geom_boxplot() 
     
# Kernel density estimates for the marginal distributions of the observed data (blue) and the m=10 densities per variable calculated from the imputed data (thin red lines) (continuous variables)
densityplot(imp)

# Check center and dispersion convergence over the ten iterations and 10 sets
plot(imp)

# Summary statistics for all 10 sets, including incomplete set. 

# Complete 
summary(frame[2:18])

# First imputed set
summary(complete(imp, action =1))

# Second imputed set
summary(complete(imp, action =2))

# Third imputed set
summary(complete(imp, action =3))

# Fourth imputed set
summary(complete(imp, action =4))

# Fifth imputed set
summary(complete(imp, action =5))

# Sixth imputed set
summary(complete(imp, action =6))

# Seventh imputed set
summary(complete(imp, action =7))

# 8th imputed set
summary(complete(imp, action =8))

# 9th imputed set
summary(complete(imp, action =9))

# 10th  imputed set
summary(complete(imp, action =10))

# Compare how well kidney involvement predicts creatinine in complete-case analysis and in pooled over 10 imputed sets
fit_comp <- lm(data = frame, creatinine ~ kidney)
summary(fit_comp)

fit <- with(data = imp, exp = lm(creatinine ~ kidney))
summary(pool.syn(fit))

# Compare how well kidney involvement predicts creatinine in complete-case analysis and in pooled over 10 imputed sets
fit <- with(data = imp, exp = glm(ent ~ anca, family = binomial))
summary(pool.syn(fit))

fit_comp <- glm(data = frame, ent ~ anca, family = binomial)
summary(fit_comp)

# Heads of some of the imputed data
head(imp$imp$creatinine)
head(imp$imp$age)
head(imp$imp$crp)
head(imp$imp$constitutional)
head(imp$imp$anca)

# Any problems?
imp$loggedEvents

# We save the imputed files in an .rda object
save(imp, file = "imputed_data.rda")

```










